Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
typo

  \maciek{Rewrite the paragraph to emphasize in the definition that requests that did not increase the counter are not included}
  We distinguish two disjoint subsequences of input $\sigma$ that arrived during the phase: $\sigma_I$ and $\sigma_E$, called \emph{internal} and \emph{external}, respectively.
  We only account for the requests to nodes that were not collocated by \TAlg at the moment of their arrival, i.e., the requests that increased a counter.
  The subsequence $\sigma_E$ contains requests to pairs that belong to the same component of \TAlg{} at the end of the phase, and $\sigma_E$ denotes the requests to pairs that did not belong to the same component of \TAlg.

>>>>

  \maciek{Rewrite the paragraph to emphasize in the definition that requests that did not increase the counter are not included}
  We distinguish two disjoint subsequences of input $\sigma$ that arrived during the phase: $\sigma_I$ and $\sigma_E$, called \emph{internal} and \emph{external}, respectively.
  We only account for the requests to nodes that were not collocated by \TAlg at the moment of their arrival, i.e., the requests that increased a counter.
  The subsequence $\sigma_E$ contains requests to pairs that belong to the same component of \TAlg{} at the end of the phase, and $\sigma_I$ denotes the requests to pairs that did not belong to the same component of \TAlg.
